%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[backend=biber,
minnames=5,
maxnames=5,
sorting=none]{biblatex}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks,pdfnewwindow]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}
\usepackage{orcidlink}
\usepackage{tikz}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif\
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\addbibresource{main.bib}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

%\tikzset{every picture/.append style={scale=1.4}}

\providecommand\mnras{\rm{MNRAS}}

\renewbibmacro{in:}{}

\renewcommand*{\bibfont}{\small}

\renewcommand*{\mkbibnamegiven}[1]{%
  \ifitemannotation{highlight}
    {\textbf{#1}}
    {#1}}

\renewcommand*{\mkbibnamefamily}[1]{%
  \ifitemannotation{highlight}
    {\textbf{#1}}
    {#1}}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape James T. Garland} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:9176557955}{+1 (917) 655-7955}
    $|$
    \faAt \hspace{.5pt} \href{mailto:james.garland@mail.utoronto.ca}{james.garland@mail.utoronto.ca}
    $|$
    \faGlobe \hspace{.5pt} \href{https://www.jamesgarland.net}{jamesgarland.net}
    $|$
    \orcidlink{0000-0003-2922-1416}
    % \\
    % \faMapMarker \hspace{.5pt} {1120 Park Ave., New York, NY 10128, USA}
\end{center}

%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeEducationHeading
      {University of Toronto}{Toronto, ON, Canada}
      {Ph.D. in Astronomy and Astrophysics}{Sep 2023 \textbf{--} Nov 2028 (Expected)}
    
    \resumeEducationHeading
      {Haverford College}{Haverford, PA, USA}
      {B.Sc. in Physics and Astronomy}{Sep 2018 \textbf{--} May 2022}
        \resumeItemListStart
            \resumeItem{Thesis: \textit{The Interplay of Tides, Bars, and Star Formation in Disk Galaxies}}
            \resumeItem{Departmental High Honors}
        \resumeItemListEnd
  \resumeSubHeadingListEnd
    
%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {American Museum of Natural History}{New York City, NY, USA}
      {Research Assistant}{Jul 2022 \textbf{--} Jul 2023}
        \resumeItemListStart
            \resumeItem{Worked with Dr. Michael Shara and the \href{https://condorarraytelescope.org/}{\color{blue}Condor Array Telescope} collaboration on identifying extragalactic novae and low-surface-brightness nova remnants in multi-epoch broad- and narrow-band images.}
            \resumeItem{Developed an automated source detection, photometry, and classification pipeline to identify transients in multi-epoch images and line-emission sources in multi-wavelength images.}
            \resumeItem{Used image correlation techniques between Condor and archival data to quantify the expansion of the nova shell around Z Cam.}
            \resumeItem{Planned observations of nova remnants for two SALT DDT proposals and analyzed the resulting RSS longslit spectra.}
            \resumeItem{Collaborated on an HST Cycle 31 proposal to measure extragalactic nova rates.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Haverford College}{Haverford, PA, USA}
      {Undergraduate Research Intern (Multiple Internships)}{Sep 2019 \textbf{--} May 2022}
        \resumeItemListStart
            \resumeItem{Worked in the research groups of Professors Karen Masters (four semesters) and Daniel Grin (two semesters), including two 10-week summer internships funded by KINSC fellowship grants.}
            \resumeItem{Studied the tidal triggering/destruction of bars in galaxies using Galaxy Zoo citizen science data. Incorporated morphological, environmental, and star formation measures to inform a more comprehensive perspective on galaxy evolution.}
            \resumeItem{Developed mock survey code to generate and observe populations of dark matter haloes under different cosmologies with simulated HI surveys. A manuscript on the limits of galaxy surveys for constraining axion dark matter models is currently in preparation.}
            \resumeItem{Presented posters and talks at multiple national, local, collaboration, and collegiate consortium meetings.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Haverford College Public Observing}{Haverford, PA, USA}
      {Co-Head (2021-2022), Volunteer}{2018 \textbf{--} 2022}
        \resumeItemListStart
            \resumeItem{Organized and ran public events for college and local communities.}
            \resumeItem{Conducted observing sessions, talks, Q\&A sessions, and observatory tours.}
            \resumeItem{Operated and trained students in the use of 8", 12", and 16" telescopes at Strawbridge Observatory.}
        \resumeItemListEnd
    
    \resumeSubheading
      {Haverford College}{Haverford, PA, USA}
      {Teaching Assistant}{Jan 2021 \textbf{--} May 2021}
        \resumeItemListStart
            \resumeItem{Held office hours, assisted with observing sessions, and graded coursework for Astronomy 101.}
        \resumeItemListEnd
    
  \resumeSubHeadingListEnd



%----------- AWARDS & HONORS -----------

\section{Awards \& Honors}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Louis B. Green Prize in Physics and Astronomy (2022):}{ Awarded to the graduating students who go above and beyond in their contributions to research and/or department culture and events.} \\ \vspace{3pt}
    
        \textbf{Chambliss Astronomy Achievement Award, Undergraduate Honorable Mention (2022):}{ Awarded for poster presented at the 240th meeting of the American Astronomical Society.} \\ \vspace{3pt}

        \textbf{KINSC Scientific Imaging Contest, Honorable Mention (2022):}{ Awarded for student-submitted images from experiments or simulations that are scientifically intriguing as well as aesthetically pleasing. \href{https://www.haverford.edu/college-communications/news/2022-kinsc-scientific-imaging-contest-winners-announced}{(\emph{\color{blue}Submission})}}
    }}
  \resumeSubHeadingListEnd

%----------- PUBLICATIONS -----------

\section{Publications}
    \vspace{3pt}

    \nocite{*}
    \printbibliography[heading=none]

%----------- TALKS & PRESENTATIONS -----------

\section{Talks \& Presentations}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        {Talk, Galaxy Zoo 15th anniversary telecon, Jul 2022.} \textit{Exploring the Roles of Galaxy Star Formation and Environment in the Tidal Triggering of Bars.} (\href{https://docs.google.com/presentation/d/15VxjLvjgd2ll7C_z6z5aoNgNm0caDdDY4YJobk2M9Ek/edit?usp=sharing}{\emph{\color{blue}Slides}}) \\ \vspace{3pt}
    
        {Poster, AAS 240th meeting, Jun 2022.} \textit{Exploring the Roles of Galaxy Star Formation and Environment in the Tidal Triggering of Bars.} (\href{https://aas240-aas.ipostersessions.com/default.aspx?s=8F-A1-98-AC-04-5C-54-D0-F4-50-96-29-2A-A2-5C-49}{\emph{\color{blue}Poster}}) \\ \vspace{3pt}

        {Talk, Galaxy Zoo biweekly telecon, Dec 2021.} \textit{Exploring the Roles of Galaxy Star Formation and Environment in the Tidal Triggering of Bars.} (\href{https://docs.google.com/presentation/d/1jzij3Ceulp25-IIE3rHtpkHmbfgnpxNTJdtfsHkyeMA/edit?usp=sharing}{\emph{\color{blue}Slides}}) \\ \vspace{3pt}

        {Talk, 32nd annual Keck Northeast Astronomy Consortium meeting, Sep 2021.} \textit{Exploring the Roles of Galaxy Star Formation and Environment in the Tidal Triggering of Bars.} (\href{https://sites.google.com/haverford.edu/knac2021/presentations?authuser=0}{\emph{\color{blue}Abstract}}, \href{https://youtu.be/3Ki3iiklxO4}{\emph{\color{blue}Recording}}) \\ \vspace{3pt}

        {Poster, Haverford KINSC Undergraduate Science Research Symposium, Sep 2021.} \textit{Exploring the Roles of Galaxy Star Formation and Environment in the Tidal Triggering of Bars.} \\ \vspace{3pt}

        {Poster, AAS 237th meeting, Jan 2021.} \textit{Can HI Observations of Low-Mass Galaxies Test Ultra-Light Axion Dark Matter?} (\href{https://baas.aas.org/pub/2021n1i149p02/release/1}{\emph{\color{blue}Abstract}}, \href{https://aas237-aas.ipostersessions.com/default.aspx?s=83-87-6E-2B-3B-93-FC-40-63-5C-44-DF-0D-54-65-42}{\emph{\color{blue}Poster}}) \\ \vspace{3pt}

        {Poster, Haverford KINSC Undergraduate Science Research Symposium, Oct 2020.} \textit{Can We Test Axion Dark Matter Models With Galaxy Surveys?} \\ \vspace{3pt}

        {Poster, 31st annual Keck Northeast Astronomy Consortium meeting, Oct 2020.} \textit{Can HI Observations of Low-Mass Galaxies Test Ultra-Light Axion Dark Matter?} (\href{https://sites.google.com/view/knac2020/posters?authuser=0}{\emph{\color{blue}Abstract}}) \\ \vspace{3pt}

        {``Lightning talk'', 2020 SDSS-IV/V Collaboration Meeting, Jun 2020.} \textit{Can HI Observations of Low-Mass Galaxies Test Ultra-Light Axion Dark Matter?}
    }}
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Technical:}{ Python, Data Reduction and Analysis, Data Visualization, Optical Telescope Operation, CCD Image Reduction, Observation Planning, Astrophotography} \\ \vspace{3pt}
        
        \textbf{Communications:}{ Proposal Writing, Scientific Writing, Science Communication, Public Outreach}
    }}
  \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

\section{Relevant Coursework}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Astronomy (Undergraduate):}{ Intro Astrophysics, Observational Astronomy, Multi-Wavelength Astronomy, Galactic Dynamics \& Mechanics (mixed undergraduate \& graduate), Gravitational Waves, Extragalactic Data Science} \\ \vspace{3pt}

        \textbf{Physics (Undergraduate):}{ Fundamental Physics I-II, Waves and Optics, Advanced Quantum Mechanics, Advanced Classical Mechanics, Advanced Electromagnetism} \\ \vspace{3pt}

        \textbf{Misc. (Undergraduate):}{ Multivariable Calculus, Linear Algebra, History of Science}
    }}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
